Carrier phase and amplitude estimation for phase shift keying using pilots and data (Appendix)

### 2012-08-21 paper2.tex
minor edits
more edits

%set sections and equation counters based on the previous document.
\setcounter{equation}{20}
\newcounter{lasteqplusone}
\setcounter{lasteqplusone}{\value{equation}}
\addtocounter{lasteqplusone}{1}
\setcounter{section}{9}
\newcounter{lastsecplusone}
\setcounter{lastsecplusone}{\value{section}}
\addtocounter{lastsecplusone}{1}

@@

\begin{lemma}~\label{lem:diffatlambdaL}
The derivative of $G_L$ exists, and is equal to zero, at $\hat{\lambda}_L$.  That is,
\[
G_L^\prime(\hat{\lambda}_L) = \frac{d G_L}{d \lambda}(\hat{\lambda}_L) = 0,
\]
\end{lemma}
\begin{IEEEproof}
Observe that 
\[
G_L(\lambda) = \frac{1}{L}\sum_{i \in P} R_i \cos(\lambda + \Phi_i) + \frac{1}{L} \sum_{i \in D} R_i \cos\sfracpart{\lambda + \Phi_i}
\] 
is differentiable everywhere except when $\fracpart{\lambda + \Phi_i} = -\tfrac{\pi}{M}$ for any $i \in D$ with $R_i > 0$.  Let $q_i$ be the smallest number from the interval $[-\tfrac{\pi}{M}, 0]$ such that
\[
 \sin(q_i) > -\frac{\rho_o \sabs{\eta}^2 R_i}{4 L \hat{\rho} \sin(\pi/M)}
\]
where $\eta = e^{-j2\pi/M} - 1$.  Observe that if $R_i > 0$ then $q_i < 0$.  Lemma~\ref{lem:fracpartlambdahatnotpi} shows that,
\[
\sabs{\sfracpart{\hat{\lambda}_L + \Phi_i}} \leq \frac{\pi}{M} + q_i
\]
for all $i \in D$.  Thus, $\sfracpart{\hat{\lambda}_L + \Phi_i} \neq -\tfrac{\pi}{M}$ for $i \in D$ when $R_i > 0$ and therefore $G_L$ is differentiable at $\hat{\lambda}_L$.

@@

\begin{lemma}\label{lem:fracpartlambdahatnotpi} Let $q_i, i \in D$ be defined as in Lemma~\ref{lem:diffatlambdaL}.  Then $\sabs{\sfracpart{\hat{\lambda}_L + \Phi_i}} \leq \frac{\pi}{M} + q_i$ for all $i \in D$.
\end{lemma}
\begin{IEEEproof}
Recall that $\{\hat{d}_i = \hat{d}_i(\hat{\theta}), i \in D\}$ defined in \eqref{eq:hatdfinxtheta} are the minimsers of the function 
\[
SS(\{d_i, i \in D\}) = A - \frac{1}{L}\sabs{Y(\{d_i, i \in D\})}^2,
\]
defined in~\eqref{eq:SSdatasymbols}. The proof now proceeds by contradiction.  Assume that 
\begin{equation}\label{eq:fraclambassumption}
\sfracpart{\hat{\lambda}_L + \Phi_k} > \frac{\pi}{M} + q_k
\end{equation}
for some $k \in D$.  Recalling the notation $e_k$ defined in Section~\ref{sec:least-squar-estim}, put $r_i = \hat{d}_i e_k$.  We will show that $SS(\{r_i, i \in D\}) < SS(\{\hat{d}_i, i \in D\})$, violating the fact that $\{\hat{d}_i, i \in D\}$ are minimisers of $SS$.  First observe that,
\begin{align*}
Y(\{ r_i, i \in D\}) = \sum_{i \in P} y_ip_i^* + \sum_{i \in D} y_i\hat{r}_i^* = \hat{Y} + \eta y_k\hat{d}_k^*.
\end{align*}
where $\eta = e^{-j2\pi/M} - 1$ and $\hat{Y} = Y(\{ \hat{d}_i, i \in D\})$.  Now,
\begin{align*}
SS&(\{r_i, i \in D\}) \\
&= A - \frac{1}{L} \sabs{ Y(\{ r_i, i \in D\}) }^2 \\
&= A - \frac{1}{L} \sabs{ \hat{Y} + \eta y_k\hat{d}_k^* }^2 \\
&= A - \frac{1}{L}\sabs{\hat{Y}}^2 - \frac{2}{L}\Re\left(\eta \hat{Y}^* y_k \hat{d}_k^* \right) -  \frac{1}{L}\sabs{ \eta y_k}^2\\
&= SS(\{\hat{d}_i, i \in D\}) - D
\end{align*}
where 
\[
D = \frac{2}{L}\Re\left(\eta \hat{Y}^* y_k \hat{d}_k^* \right) +  \frac{1}{L}\sabs{ \eta y_k }^2.
\]
Now $\frac{1}{L}\hat{Y} = \hat{a} = \hat{\rho} e^{j\hat{\theta}}$ from~\eqref{eq:hata} and using~\eqref{eq:yethetadhat},
\[
\frac{1}{L} \hat{Y}^* y_k \hat{d}_k^* = \hat{\rho} \rho_0 R_k e^{j\sfracpart{\hat{\lambda}_L + \Phi_k}},
\]
so that
\begin{equation}\label{eq:Ddefn}
D = 2 \hat{\rho} \rho_0 R_k \Re\left( \eta e^{j\sfracpart{\hat{\lambda}_L + \Phi_k}}\right) + \frac{1}{L}\sabs{\eta}^2\rho_0^2 R_k^2.
\end{equation}
Let $v = \sfracpart{\hat{\lambda}_L + \Phi_k} - \tfrac{\pi}{M}$ so that
\begin{align*}
\eta e^{j\sfracpart{\hat{\lambda}_L + \Phi_k}} &= (e^{-j2\pi/M} - 1) e^{j \pi/M} e^{jv} \\
&= (e^{-j\pi/M} - e^{j\pi/M}) e^{jv} \\
&= -2 \sin(\tfrac{\pi}{M}) e^{j ( v + \pi/2) }
\end{align*}
and
\begin{align*}
\Re\left( \eta e^{j\sfracpart{\hat{\lambda}_L + \Phi_k}}\right) &= -2 \sin(\tfrac{\pi}{M}) \cos(v + \tfrac{\pi}{2}) \\
 &= 2 \sin(\tfrac{\pi}{M}) \sin(v),
\end{align*}
Because we assumed~\eqref{eq:fraclambassumption}, it follows that $0 > v > q_k$ and, from the definition of $q_k$,
\[
0 > \sin(v) > -\frac{\rho_o \sabs{\eta}^2 R_i}{4 L \hat{\rho} \sin(\pi/M)}.
\]
Subtituting this into~\eqref{eq:Ddefn} gives $D > 0$, but then $SS(\{r_i, i \in D\}) < SS(\{\hat{d}_i, i \in D\})$, violating the fact that $\{\hat{d}_i, i \in D\}$ are minimisers of $SS$.  Thus,~\eqref{eq:fraclambassumption} is false.

@@

\begin{lemma}\label{lem:Qconv}
Let $Q_L(\lambda) = \expect R_L(\lambda) - \expect R_L(0)$ where the function $R_L$ is defined in~\eqref{eq:RLdef}.  Then,
\[ 
\sqrt{L} Q_L(\hat{\lambda}_L) = \sqrt{L} \hat{\lambda}_L\big( p + Hd  + o_P(1) \big)
\]
where $p, d$ and $H$ are real numbers defined in the statements of Thereoms~\ref{thm:consistency}~and~\ref{thm:normality} and $o_P(1)$ denotes a number converging in probability to zero as $L\rightarrow\infty$.
\end{lemma}
\begin{IEEEproof}
We have
\[
Q_L(\lambda) = \expect R_L(\lambda) - \expect R_L(0) = \tfrac{\sabs{P}}{L} k_1(\lambda) + \tfrac{\sabs{D}}{L} k_2(\lambda)
\]
where
\begin{align}
k_1(\lambda) &= \expect R_1\big( \sin(\lambda + \Phi_1) - \sin(\Phi_1) \big), \;\;\; \text{and} \nonumber\\
k_2(\lambda) &= \expect R_1\big( \sin\fracpart{\lambda + \Phi_1} - \sin\fracpart{\Phi_1} \big). \label{eq:k2def}
\end{align}
We analyse $k_1(\lambda)$ first.  By a Taylor expansion of $\sin(\lambda + \Phi_1)$ about $\lambda = 0$,
\[
\sin(\lambda + \Phi_1) - \sin(\Phi_1) = \lambda \big( \cos(\Phi_1) + \zeta(\lambda) \big),
\]
where $\zeta$ is a continuous function with $\zeta(0) = 0$.  So,
\begin{align*}
k_1(\lambda) &= \expect R_1\lambda(\cos(\Phi_1) \; + \; \zeta(\lambda)) \\
&= \lambda \big( 1 \; + \; \zeta(\lambda) \expect R_1 \big) 
\end{align*}
since $h_1(0) = \expect R_1\cos(\Phi_1) = 1$ because $w_1$ has zero mean.  Because $\hat{\lambda}_L$ converges almost surely to zero as $L \rightarrow\infty$, then $\zeta(\hat{\lambda}_L)$ converges almost surely (and therefore also in probability) to zero as $L \rightarrow\infty$, i.e. $\zeta(\hat{\lambda}_L) = o_P(1)$.  So, 
\[
k_1(\hat{\lambda}_L) = \hat{\lambda}_L \big( 1 \; + \; \zeta(\hat{\lambda}_L) \expect R_1 \big) = \hat{\lambda}_L \big( 1  + o_P(1)\big)
\]
because $\expect R_1$ is finite.  Lemma~\ref{lem:k2conv} shows that $k_2(\hat{\lambda}_L) = \hat{\lambda}_L ( H + o_P(1) )$.  So,
\begin{align*}
Q_L(\hat{\lambda}_L) &=  \tfrac{\sabs{P}}{L} \hat{\lambda}_L \big( 1  + o_P(1)\big)  + \tfrac{\sabs{D}}{L} \hat{\lambda}_L ( H + o_P(1) ) \\
&= \hat{\lambda}_L \left( \tfrac{\sabs{P}}{L}  + \tfrac{\sabs{D}}{L} H + o_P(1) \right) \\
&= \hat{\lambda}_L \left( p  + d H + o_P(1) \right),
\end{align*}
since $\frac{\sabs{P}}{L} \rightarrow p$ and $\frac{\sabs{D}}{L} \rightarrow d$ as $L \rightarrow \infty$.  The lemma follows by multiplying both sides of the above equation by $\sqrt{L}$.
\end{IEEEproof}

@@

\begin{lemma}\label{lem:expRvlamphi}
$W(\lambda) =  \lambda(H_1 + \gamma(\lambda))$ where $\gamma$ is a continuous function with $\gamma(0) = 0$.
\end{lemma}
\begin{IEEEproof}
In this lemma, as in Lemma~\ref{lem:k2conv}, we work under the assumption that $0 \leq \lambda < \frac{\pi}{M}$.  An analgous argument follows when $-\tfrac{\pi}{M} \leq \lambda < 0$.  Recalling that $f(r,\phi)$ is the joint pdf of $R_1$ and $\Phi_1$, 
\begin{align}
W(\lambda) &= \expect R_1 v(\lambda, \Phi_1) \nonumber  \\
&= \int_0^{2\pi}\int_{0}^\infty r v(\lambda, \phi) f(r,\phi) dr d\phi \nonumber  \\ 
&= \int_0^{2\pi} v(\lambda, \phi) g(\phi) d\phi \nonumber \\
&= \sum_{k \in \ints} \int_0^{2\pi} v_k(\lambda, \phi) g(\phi) d\phi. \label{eq:Winfsum}
\end{align}
Now, for $k = 1, \dots, M-1$ we have $0 < \psi_{k-1} < \psi_k < 2\pi$, and so, using~\eqref{eq:vk},
\begin{align*}
\int_0^{2\pi} v_k(\lambda, \phi) &g(\phi) d\phi = \int_{\psi_{k-1}}^{\psi_{k}} v_k(\lambda, \phi) g(\phi) d\phi \\
&= \lambda a_k(\lambda) + \lambda b_k(\lambda) + \lambda c_k(\lambda),
\end{align*}
where, for $k = 1, \dots, M-1$,
\begin{equation}\label{eq:ak}
a_k(\lambda) = \int_{\psi_k-\lambda}^{\psi_k}\eta_k(\lambda, \phi) g(\phi) d\phi,
\end{equation}
\[
b_k(\lambda) = \zeta_k(\lambda) \int_{\psi_{k-1}}^{\psi_k -\lambda}g(\phi) d\phi,
\]
\begin{equation}\label{eq:ck}
c_k(\lambda) = \frac{1}{\lambda} \int_{\psi_{k} - \lambda}^{\psi_{k}} s_k(\phi) g(\phi) d\phi.
\end{equation}
Both $a_k(\lambda)$ and $b_k(\lambda)$ converge to zero as $\lambda$ goes to zero, and, since $g$ is continuous at $\psi_k = \tfrac{2\pi}{M}k + \tfrac{\pi}{M}$ for each $k = 0, 1, \dots, M-1$ by Proposition~\ref{prop:gg2cont} in~\cite{McKilliam_leastsqPSKpilotsdata_2012}, it follows $c_k(\lambda)$ converges to 
\[
s_k(\psi_k)g(\psi_k) = -2\sin(\tfrac{\pi}{M}) g(\tfrac{2\pi}{M}k + \tfrac{\pi}{M})
\]
as $\lambda$ goes to zero from above.  We are only interested in the limit from above because we are working under the assumption that $0 \leq \lambda < \frac{\pi}{M}$.  The analgous argument when $-\tfrac{\pi}{M} \leq \lambda < 0$ would involve limits as $\lambda$ approaches zero from below.

@@

\begin{lemma}\label{lem:convdistGLdash}
The distribution of $\sqrt{L}R_L(0)$ converges to the normal with zero mean and variance $pA_1 + dA_2$.
\end{lemma}
\begin{IEEEproof}
Observe that 
\[
\sqrt{L} R_L(0) = \frac{1}{\sqrt{L}} \sum_{i \in P} R_i \sin(\Phi_i) + \frac{1}{\sqrt{L}} \sum_{i \in D} R_i \sin\sfracpart{\Phi_i}.
\]
From the standard central limit the distribution of
\[
\frac{1}{\sqrt{L}} \sum_{i \in P} R_i \sin(\Phi_i) = \sqrt{\frac{\sabs{P}}{L}} \frac{1}{\sqrt{\sabs{P}}} \sum_{i \in P} R_i \sin(\Phi_i) 
\]
converges to the normal with mean $\sqrt{p}\expect R_1 \sin(\Phi_1) = 0$ as a result of~\eqref{eq:expectImpartRphi}, and variance
\[
p A_1 = p \expect R_1^2 \sin^2(\Phi_1).
\]
Similarly, the distribution of 
\[ 
\frac{1}{\sqrt{L}} \sum_{i \in D} R_i \sin\fracpart{\Phi_i} = \sqrt{\frac{\sabs{D}}{L}} \frac{1}{\sqrt{\sabs{D}}} \sum_{i \in D} R_i \sin\fracpart{\Phi_i} 
\]
converges to the normal with mean $\sqrt{d}\expect R_1 \sin\fracpart{\Phi_1} = 0$ as a result of Lemma~\ref{lem:expectImRfracpart}, and variance
\[
d A_2 = d \expect R_1^2 \sin^2\fracpart{\Phi_1}.
\]
\end{IEEEproof}

>>>>

%set sections and equation counters based on the previous document.
\setcounter{equation}{21}
\newcounter{lasteqplusone}
\setcounter{lasteqplusone}{\value{equation}}
\addtocounter{lasteqplusone}{1}
\setcounter{section}{9}
\newcounter{lastsecplusone}
\setcounter{lastsecplusone}{\value{section}}
\addtocounter{lastsecplusone}{1}

@@

\begin{lemma}~\label{lem:diffatlambdaL}
The derivative of $G_L$ exists, and is equal to zero, at $\hat{\lambda}_L$.  That is,
\[
G_L^\prime(\hat{\lambda}_L) = \frac{d G_L}{d \lambda}(\hat{\lambda}_L) = 0.
\]
\end{lemma}
\begin{IEEEproof}
Observe that 
\[
G_L(\lambda) = \frac{1}{L}\sum_{i \in P} R_i \cos(\lambda + \Phi_i) + \frac{1}{L} \sum_{i \in D} R_i \cos\sfracpart{\lambda + \Phi_i}
\] 
is differentiable everywhere except when $\fracpart{\lambda + \Phi_i} = -\tfrac{\pi}{M}$ for any $i \in D$ with $R_i > 0$.  Let $q_i$ be the smallest number from the interval $[-\tfrac{\pi}{M}, 0]$ such that
\[
 \sin(q_i) > -\frac{\rho_o \sabs{\eta}^2 R_i}{4 L \hat{\rho} \sin(\pi/M)}
\]
where $\eta = e^{-j2\pi/M} - 1$.  Observe that if $R_i > 0$ then $q_i < 0$.  Lemma~\ref{lem:fracpartlambdahatnotpi} shows that,
\[
\sabs{\sfracpart{\hat{\lambda}_L + \Phi_i}} \leq \frac{\pi}{M} + q_i
\]
for all $i \in D$.  Thus, $\sfracpart{\hat{\lambda}_L + \Phi_i} \neq -\tfrac{\pi}{M}$ for $i \in D$ when $R_i > 0$ and therefore $G_L$ is differentiable at $\hat{\lambda}_L$.

@@

\begin{lemma}\label{lem:fracpartlambdahatnotpi} Let $q_i, i \in D$ be defined as in Lemma~\ref{lem:diffatlambdaL}.  Then $\sabs{\sfracpart{\hat{\lambda}_L + \Phi_i}} \leq \frac{\pi}{M} + q_i$ for all $i \in D$.
\end{lemma}
\begin{IEEEproof}
Recall that $\{\hat{d}_i = \hat{d}_i(\hat{\theta}), i \in D\}$ defined in \eqref{eq:hatdfinxtheta} are the minimsers of the function 
\[
SS(\{d_i, i \in D\}) = A - \frac{1}{L}\sabs{Y(\{d_i, i \in D\})}^2,
\]
defined in~\eqref{eq:SSdatasymbols}. The proof now proceeds by contradiction.  Assume that 
\begin{equation}\label{eq:fraclambassumption}
\sfracpart{\hat{\lambda}_L + \Phi_k} > \frac{\pi}{M} + q_k
\end{equation}
for some $k \in D$.  Recalling the notation $e_k$ defined in Section~\ref{sec:least-squar-estim}, put $r_i = \hat{d}_i e_k$.  We will show that 
\[
SS(\{r_i, i \in D\}) < SS(\{\hat{d}_i, i \in D\}),
\]
violating the fact that $\{\hat{d}_i, i \in D\}$ are minimisers of $SS$.  First observe that,
\begin{align*}
Y(\{ r_i, i \in D\}) = \sum_{i \in P} y_ip_i^* + \sum_{i \in D} y_i\hat{r}_i^* = \hat{Y} + \eta y_k\hat{d}_k^*,
\end{align*}
where $\eta = e^{-j2\pi/M} - 1$ and $\hat{Y} = Y(\{ \hat{d}_i, i \in D\})$.  Now,
\begin{align*}
SS&(\{r_i, i \in D\}) \\
&= A - \frac{1}{L} \sabs{ Y(\{ r_i, i \in D\}) }^2 \\
&= A - \frac{1}{L} \sabs{ \hat{Y} + \eta y_k\hat{d}_k^* }^2 \\
&= A - \frac{1}{L}\sabs{\hat{Y}}^2 - \frac{2}{L}\Re\left(\eta \hat{Y}^* y_k \hat{d}_k^* \right) -  \frac{1}{L}\sabs{ \eta y_k}^2\\
&= SS(\{\hat{d}_i, i \in D\}) - D,
\end{align*}
where 
\[
D = \frac{2}{L}\Re\left(\eta \hat{Y}^* y_k \hat{d}_k^* \right) +  \frac{1}{L}\sabs{ \eta y_k }^2.
\]
Now $\frac{1}{L}\hat{Y} = \hat{a} = \hat{\rho} e^{j\hat{\theta}}$ from~\eqref{eq:hata} and using~\eqref{eq:yethetadhat},
\[
\frac{1}{L} \hat{Y}^* y_k \hat{d}_k^* = \hat{\rho} \rho_0 R_k e^{j\sfracpart{\hat{\lambda}_L + \Phi_k}},
\]
so that
\begin{equation}\label{eq:Ddefn}
D = 2 \hat{\rho} \rho_0 R_k \Re\left( \eta e^{j\sfracpart{\hat{\lambda}_L + \Phi_k}}\right) + \frac{1}{L}\sabs{\eta}^2\rho_0^2 R_k^2.
\end{equation}
Let $v = \sfracpart{\hat{\lambda}_L + \Phi_k} - \tfrac{\pi}{M}$ so that
\begin{align*}
\eta e^{j\sfracpart{\hat{\lambda}_L + \Phi_k}} &= (e^{-j2\pi/M} - 1) e^{j \pi/M} e^{jv} \\
&= (e^{-j\pi/M} - e^{j\pi/M}) e^{jv} \\
&= -2 \sin(\tfrac{\pi}{M}) e^{j ( v + \pi/2) },
\end{align*}
and
\begin{align*}
\Re\left( \eta e^{j\sfracpart{\hat{\lambda}_L + \Phi_k}}\right) &= -2 \sin(\tfrac{\pi}{M}) \cos(v + \tfrac{\pi}{2}) \\
 &= 2 \sin(\tfrac{\pi}{M}) \sin(v),
\end{align*}
Because we assumed~\eqref{eq:fraclambassumption}, it follows that $0 > v > q_k$ and, from the definition of $q_k$,
\[
0 > \sin(v) > -\frac{\rho_o \sabs{\eta}^2 R_i}{4 L \hat{\rho} \sin(\pi/M)}.
\]
Subtituting this into~\eqref{eq:Ddefn} gives $D > 0$, but then $SS(\{r_i, i \in D\}) < SS(\{\hat{d}_i, i \in D\})$, violating the fact that $\{\hat{d}_i, i \in D\}$ are minimisers of $SS$.  Thus,~\eqref{eq:fraclambassumption} is false.

@@

\begin{lemma}\label{lem:Qconv}
Let $Q_L(\lambda) = \expect R_L(\lambda) - \expect R_L(0)$ where the function $R_L$ is defined in~\eqref{eq:RLdef}.  Then,
\[ 
\sqrt{L} Q_L(\hat{\lambda}_L) = \sqrt{L} \hat{\lambda}_L\big( p + Hd  + o_P(1) \big)
\]
where $p, d$ and $H$ are real numbers defined in the statements of Thereoms~\ref{thm:consistency}~and~\ref{thm:normality} and $o_P(1)$ denotes a number converging in probability to zero as $L\rightarrow\infty$.
\end{lemma}
\begin{IEEEproof}
We have
\[
Q_L(\lambda) = \expect R_L(\lambda) - \expect R_L(0) = \tfrac{\sabs{P}}{L} k_1(\lambda) + \tfrac{\sabs{D}}{L} k_2(\lambda)
\]
where
\begin{align}
k_1(\lambda) &= \expect R_1\big( \sin(\lambda + \Phi_1) - \sin(\Phi_1) \big), \;\;\; \text{and} \nonumber\\
k_2(\lambda) &= \expect R_1\big( \sin\fracpart{\lambda + \Phi_1} - \sin\fracpart{\Phi_1} \big). \label{eq:k2def}
\end{align}
We analyse $k_1(\lambda)$ first.  By a Taylor expansion of $\sin(\lambda + \Phi_1)$ about $\lambda = 0$,
\[
\sin(\lambda + \Phi_1) - \sin(\Phi_1) = \lambda \big( \cos(\Phi_1) + \zeta(\lambda) \big),
\]
where $\zeta$ is a continuous function with $\zeta(0) = 0$.  So,
\begin{align*}
k_1(\lambda) &= \expect R_1\lambda(\cos(\Phi_1) \; + \; \zeta(\lambda)) \\
&= \lambda \big( 1 \; + \; \zeta(\lambda) \expect R_1 \big) 
\end{align*}
since $h_1(0) = \expect R_1\cos(\Phi_1) = 1$ as a result of~\eqref{eq:expectRepartRphi}.  Because $\hat{\lambda}_L$ converges almost surely to zero as $L \rightarrow\infty$, then $\zeta(\hat{\lambda}_L)$ converges almost surely (and therefore also in probability) to zero as $L \rightarrow\infty$, i.e. $\zeta(\hat{\lambda}_L) = o_P(1)$.  So, 
\[
k_1(\hat{\lambda}_L) = \hat{\lambda}_L \big( 1 \; + \; \zeta(\hat{\lambda}_L) \expect R_1 \big) = \hat{\lambda}_L \big( 1  + o_P(1)\big)
\]
because $\expect R_1$ is finite.  Lemma~\ref{lem:k2conv} shows that $k_2(\hat{\lambda}_L) = \hat{\lambda}_L ( H + o_P(1) )$.  So,
\begin{align*}
Q_L(\hat{\lambda}_L) &=  \tfrac{\sabs{P}}{L} \hat{\lambda}_L \big( 1  + o_P(1)\big)  + \tfrac{\sabs{D}}{L} \hat{\lambda}_L ( H + o_P(1) ) \\
&= \hat{\lambda}_L \left( \tfrac{\sabs{P}}{L}  + \tfrac{\sabs{D}}{L} H + o_P(1) \right) \\
&= \hat{\lambda}_L \left( p  + d H + o_P(1) \right),
\end{align*}
since $\frac{\sabs{P}}{L} \rightarrow p$ and $\frac{\sabs{D}}{L} \rightarrow d$ as $L \rightarrow \infty$.  The lemma follows by multiplying both sides of the above equation by $\sqrt{L}$.
\end{IEEEproof}

@@

\begin{lemma}\label{lem:expRvlamphi}
$W(\lambda) =  \lambda(H_1 + \gamma(\lambda))$ where $\gamma$ is a continuous function with $\gamma(0) = 0$.
\end{lemma}
\begin{IEEEproof}
In this lemma, as in Lemma~\ref{lem:k2conv}, we work under the assumption that $0 \leq \lambda < \frac{\pi}{M}$.  An analgous argument follows when $-\tfrac{\pi}{M} \leq \lambda < 0$.  Recalling that $f(r,\phi)$ is the joint pdf of $R_1$ and $\Phi_1$, 
\begin{align}
W(\lambda) &= \expect R_1 v(\lambda, \Phi_1) \nonumber  \\
&= \int_0^{2\pi}\int_{0}^\infty r v(\lambda, \phi) f(r,\phi) dr d\phi \nonumber  \\ 
&= \int_0^{2\pi} v(\lambda, \phi) g(\phi) d\phi \nonumber \\
&= \sum_{k \in \ints} \int_0^{2\pi} v_k(\lambda, \phi) g(\phi) d\phi, \label{eq:Winfsum}
\end{align}
where $g$ is defined in the statement of Theorem~\ref{thm:normality}
Now, for $k = 1, \dots, M-1$ we have $0 < \psi_{k-1} < \psi_k < 2\pi$, and so, using~\eqref{eq:vk},
\begin{align*}
\int_0^{2\pi} v_k(\lambda, \phi) &g(\phi) d\phi = \int_{\psi_{k-1}}^{\psi_{k}} v_k(\lambda, \phi) g(\phi) d\phi \\
&= \lambda a_k(\lambda) + \lambda b_k(\lambda) + \lambda c_k(\lambda),
\end{align*}
where, for $k = 1, \dots, M-1$,
\begin{equation}\label{eq:ak}
a_k(\lambda) = \int_{\psi_k-\lambda}^{\psi_k}\eta_k(\lambda, \phi) g(\phi) d\phi,
\end{equation}
\[
b_k(\lambda) = \zeta_k(\lambda) \int_{\psi_{k-1}}^{\psi_k -\lambda}g(\phi) d\phi,
\]
\begin{equation}\label{eq:ck}
c_k(\lambda) = \frac{1}{\lambda} \int_{\psi_{k} - \lambda}^{\psi_{k}} s_k(\phi) g(\phi) d\phi.
\end{equation}
Both $a_k(\lambda)$ and $b_k(\lambda)$ converge to zero as $\lambda$ goes to zero, and, since $g$ is continuous at $\psi_k = \tfrac{2\pi}{M}k + \tfrac{\pi}{M}$ for each $k = 0, 1, \dots, M-1$ by Proposition~\ref{prop:gg2cont} in~\cite{McKilliam_leastsqPSKpilotsdata_2012}, it follows that $c_k(\lambda)$ converges to 
\[
s_k(\psi_k)g(\psi_k) = -2\sin(\tfrac{\pi}{M}) g(\tfrac{2\pi}{M}k + \tfrac{\pi}{M})
\]
as $\lambda$ goes to zero from above.  We are only interested in the limit from above because we are working under the assumption that $0 \leq \lambda < \frac{\pi}{M}$.  The analgous argument when $-\tfrac{\pi}{M} \leq \lambda < 0$ would involve limits as $\lambda$ approaches zero from below.

@@

\begin{lemma}\label{lem:convdistGLdash}
The distribution of $\sqrt{L}R_L(0)$ converges to the normal with zero mean and variance $pA_1 + dA_2$.
\end{lemma}
\begin{IEEEproof}
Observe that $\sqrt{L} R_L(0) = C_L + D_L$ where
\[
C_L = \frac{1}{\sqrt{L}} \sum_{i \in P} R_i \sin(\Phi_i), \qquad D_L = \frac{1}{\sqrt{L}} \sum_{i \in D} R_i \sin\sfracpart{\Phi_i}.
\]
From the standard central limit theorem the distribution of $C_L$ converges to the normal with mean $\sqrt{p}\expect R_1 \sin(\Phi_1) = 0$ as a result of~\eqref{eq:expectImpartRphi}, and variance
\[
p A_1 = p \expect R_1^2 \sin^2(\Phi_1).
\]
Similarly, the distribution of $D_L$ converges to the normal with mean $\sqrt{d}\expect R_1 \sin\fracpart{\Phi_1} = 0$ as a result of Lemma~\ref{lem:expectImRfracpart}, and variance
\[
d A_2 = d \expect R_1^2 \sin^2\fracpart{\Phi_1}.
\]
The lemma holds because $C_L$ and $D_L$ are independent. 
\end{IEEEproof}

\begin{lemma}\label{lem:expectImRfracpart}
$\expect R_1 \sin\fracpart{\Phi_1} = 0$.
\end{lemma}
\begin{IEEEproof}
Recalling that $f(r,\phi)$ is the joint pdf of $R_1$ and $\Phi_1$, we have
\begin{align*}
\expect R_1 \sin\fracpart{\Phi_1} &= \int_{0}^{2\pi} \int_{0}^\infty r \sin\fracpart{\phi} f(r,\phi) dr d\phi \\
&= \int_{-\pi}^{\pi} \sin\fracpart{\phi} g(\phi) d\phi,
\end{align*}
where $g$ is defined in the statement of Theorem~\ref{thm:normality} and the change in bounds from $0, 2\pi$ to $-\pi,\pi$ is valid because both $\sin\fracpart{\phi}$ and $g(\phi)$ have period $2\pi$.  Propostion~\ref{prop:gg2cont} in \cite{McKilliam_leastsqPSKpilotsdata_2012} shows that $g$ is even on $(-\pi,\pi)$.  Also $\sin\fracpart{\cdot}$ has period $\tfrac{2\pi}{M}$ and is odd on $(-\frac{\pi}{M}, \tfrac{\pi}{M})$.  So, for any $k \in \ints$ and $\phi \in (-\tfrac{\pi}{M}, 0)$,
\[
g(-\phi + k \tfrac{\pi}{M}) = g(\phi - k \tfrac{\pi}{M})
\]
and
\[
\sin\fracpart{-\phi + k \tfrac{\pi}{M}} = -\sin\fracpart{\phi - k \tfrac{\pi}{M}}.
\]
Now,
\begin{align*}
I_k &= \int_{-(k+1)\tfrac{\pi}{M}}^{-k\tfrac{\pi}{M}}\sin\fracpart{\phi} g(\phi) d\phi + \int_{k\tfrac{\pi}{M}}^{(k+1)\tfrac{\pi}{M}}\sin\fracpart{\phi} g(\phi) d\phi \\
&= \int_{-\tfrac{\pi}{M}}^{0}\sin\fracpart{\phi -  k\tfrac{\pi}{M}} g(\phi - k\tfrac{\pi}{M}) d\phi \\
&\hspace{1cm}+ \int_{0}^{\tfrac{\pi}{M}}\sin\fracpart{\phi + k\tfrac{\pi}{M}} g(\phi + k\tfrac{\pi}{M}) d\phi \\
&= 0
\end{align*}
for all integers $k$ because
\begin{align*}
\int_{0}^{\tfrac{\pi}{M}}&\sin\fracpart{\phi + k\tfrac{\pi}{M}} g(\phi + k\tfrac{\pi}{M}) d\phi \\
&= \int_{-\tfrac{\pi}{M}}^{0}\sin\fracpart{-\phi + k\tfrac{\pi}{M}} g(-\phi + k\tfrac{\pi}{M}) d\phi \\
&= -\int_{-\tfrac{\pi}{M}}^{0}\sin\fracpart{\phi - k\tfrac{\pi}{M}} g(\phi - k\tfrac{\pi}{M}) d\phi.
\end{align*}
Observe that the sets
\[
 [-(k+1)\tfrac{\pi}{M},-k\tfrac{\pi}{M}] \cup [k\tfrac{\pi}{M},(k+1)\tfrac{\pi}{M}], \;\;\; k = 0, \dots, M-1
\]
partition $[-\pi, \pi]$, and so
\[
\expect R_1 \sin\fracpart{\Phi_1} = \int_{-\pi}^{\pi} \sin\fracpart{\phi} g(\phi) d\phi = \sum_{k=0}^{M-1} I_k = 0.
\]
\end{IEEEproof}

\begin{lemma}\label{lem:empiricprocforrho} Let $T_L(\lambda) = \expect G_L(\lambda)$.  Then
\[
\sqrt{L}\big( G_L(\hat{\lambda}_L) - T_L(\hat{\lambda}_L) \big) = o_P(1) + X_L,
\]
where $X_L = \sqrt{L} \big( G_L(0) - T_L(0) \big)$.
\end{lemma}
\begin{IEEEproof}
Let
\begin{equation}\label{eq:YLdef}
Y_L(\lambda) = \sqrt{L}\big( G_L(\hat{\lambda}_L) - T_L(\hat{\lambda}_L) \big) - X_L
\end{equation}
so that
\[
\sqrt{L}\big( G_L(\hat{\lambda}_L) - T_L(\hat{\lambda}_L) \big) = Y_L(\hat{\lambda}_L) + X_L
\]
Lemma~\ref{lem:ZYLempiricproc} in Section~\ref{sec:an-empirical-process} shows that for any $\delta > 0$ and $\nu > 0$, there exists $\epsilon > 0$ such that
\[
\Pr\left\{ \sup_{\sabs{\lambda}<\epsilon}\sabs{Y_L(\lambda)} > \delta  \right\} < \nu.
\]
The proof now follows by an argument analogous to that in Lemma~\ref{lem:empiricprocc}.
\end{IEEEproof}
